Verifying Demonstrations

### 2018-02-27 paper/TimeStamp.tex
Adds description of blockchain, TS

\mode*
\section{Building blocks}%
\label{Primitives}\label{BuildingBlocks}

\dots

\input{ZKPK.tex}
\input{ZK-anon-cred.tex}
%\input{P-signatures.tex}
\input{DistanceBounding.tex}
\input{LocationsProofs.tex}

\subsection{Timestamping storage: blockchains}%
\label{StorageProperties}

>>>>

\subsection{Time-stamping service, or, blockchains}%
\label{StorageProperties}

\NewCryptoScheme{\TS}{TS}
\NewAlgorithm{\TSget}{\TS.\!Get}
\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
\NewAlgorithm{\TSverify}{\TS.\!Verify}
\NewAlgorithm{\TStime}{\TS.\!Time}

We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
\(\TSstamp\) and \(\TStime\) such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is 
    difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
    \(\TSverify[x, \pi]\to 1\) and \(\TStime[\pi] = t\).
\end{itemize}

With these building blocks we can ensure that a message \(m\) was created within 
the time interval \(\interval{t_0}{t_1}\).
After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping 
service to get \(\pi_{t_1}\gets \TSstamp[h]\).

Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created 
within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
\(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land 
  \TStime[\pi_{t_1}] = t_1\).

We can instantiate \(\TS\) using a blockchain.
The \(\TSstamp[x]\) algorithm will simply include \(x\)

\(\TSget\) will return the hash of the current head of the chain.
This value is difficult to predict since it depends on all submitted 
transactions.
This forces us to make the assumption that the adversary cannot control 
\emph{all} transactions that are submitted to the blockchain.
As long as one non-adversarial transaction is submitted it will be 
unpredictable.
